---
title: "p8105_hw5_hw2849"
author: "Haotian Wu"
date: "11/15/2021"
output: github_document
---

```{r setup,  include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%",
  dpi = 300
)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("./homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")
  
baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), ## number of unsolved
    n = n() ## total number of homicide
  )

baltimore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), 
            n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities!

First off, write a function

```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"), 
      n = n() 
    )
  
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved), 
              n = city_summary %>% pull(n))
  
  return(city_test)
  
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()

```

Now, let's iterate across all cities

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Try to make a plot showing estimates and confidence intervals

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```

```{r}
## another approach by map2

homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r}
files = list.files("./data/", full.names = TRUE) %>% ## import files with relative path
  map(read_csv) ## iterate over file names

for (i in 1:20) { ## separate control and experiment
  if (i < 11) { ## add arm con and relative study id
    files[[i]] <- files[[i]] %>% 
      mutate(arm = "Con", 
             study_id = i)
  } else if (i > 10) { ## add arm exp and add relative study id
    files[[i]] <- files[[i]] %>% 
      mutate(arm = "Exp", 
             study_id = i - 10)
  }
}

final_df = files %>% 
  bind_rows() %>% ## stack each study into one data frame
  pivot_longer( ## make a readable table
    week_1:week_8,
    names_to = "week",
    values_to = "obs_value"
  ) %>% 
  mutate( ## tidy week and study_id variable
   week = str_remove(week, "week_"),
   week = as.numeric(week),
   study_id = as.character(study_id)
  ) %>% 
  print()
```

First, using `list.files` to import the list of files and file names, then using `map` to read all .csv files with relative path, and saved to `files`. Next, writing a function to separate the control and experiment, and adding `study_id` for each subject. Lastly, stack each subject into one data frame `final_df` and tidy the data.  

Now, make a spaghetti plot showing trends on observations for each subject over time.

```{r}
final_df %>% 
  ggplot(aes(x = week, y = obs_value, color = arm, type = study_id)) + 
  geom_line() + 
  labs(
    title = "Observations on each subject over time stratified by study arm",
    x = "Week", 
    y = "Observation") + 
  theme(
    legend.position = "bottom", 
    plot.title = element_text(size = 11))
```

From the spaghetti plot, we observed that generally participants assigned to `exp` group have a higher value than those who assigned to `con` group over time. In addition, `exp` group shows an increasing trend while `con` group remain constant across the study period.

## Problem 3

Load and tidy `iris`, and filling in the missing values. 

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

## filling the missing values
clean_data = function(x){ 
  
  if (is.numeric(x)) { ## if the value is NA, replace by mean of x
    x = replace_na(x, mean(x, na.rm = TRUE))
  } 
  
  else if (is.character(x)) { ## if the species is NA replace by virginica
    x = replace_na(x, "virginica")
  }
}

iris = map_df(iris_with_missing, clean_data) %>% 
  as_tibble() %>% print()
```

To filling the missing values for `iris`, we consider in two cases: numeric variables and character variables. And so we wrote a function that filling in missing values with the mean of non-missing values; and replace `NA` with `virginica` for character variables. 




